A significance test in forward stepwise regression

### 2014-04-08 paper/paper.tex
quadratic almost done

\begin{figure}
\label{fig:curved}
\begin{center}
\resizebox{!}{3in}{\input{../figs/curved.pdf_edit_tex}}
\end{center}
A generic selection event, given by the intersection of a list
of quadratic inequalities. \end{figure}

The slice for any particular inequality is
$$
\begin{aligned}
\lefteqn{
\left\{t: (y+t\eta)^T Q_i (y+t \cdot \eta) + a_i^T(y+t \cdot \eta) \leq b_i\right\}} \\
 & \qquad = \left\{t: t^2 \cdot \eta^TQ_i\eta + t \cdot(2 y^TQ_i\eta + a_i^T\eta) + y^TQ_iy + a_i^Ty - b_i \leq 0 \right\} \\
\end{aligned}
$$
This can be computed easily, and results in either the empty, a single interval (possibly infinite) or the union of 
two disjoint infinite intervals. The intersection over all $I(s)$ is therefore easily computable.
This yields an easily computable form for the slice
\begin{equation}
\label{eq:slice}
\{g^*(y)=g, \eta(g^*(y))=\eta\}.
\end{equation}

\subsection{Relation to covariance test}

Consider the simple case for the first covariate to enter the model.
In this case the covariance test statistic is $T = \lambda_1(\lambda_1 - M)$.
\todo Does $M = \lambda_2$? Check proof, now that statistic has changed

This is Lemma 5 from \cite{significance:lasso}.

  \item As in LTTT, $T = \lambda_1 (\lambda_1 - M)$ and $M = \lambda_2$
  \item Convergence to the limiting Exp(1) distribution is too slow
    \[
      \frac{P(\chi_k / w_g \geq m + t/m)}{P(\chi_k / w_g \geq m)} \to e^{-t} \text{ as } m \to \infty
    \]
    (when the group achieving $\lambda_1$ is group $g$ and has rank $k$)
  \item The limiting distribution only depends on $T$, but we also observe $M$
  \item Let's just try the ratio (conditional $\chi_k$ tail probability) evaluated at $T$ and $M$ (it works better)
  \item Going one step further, instead of using the approximation (see LTTT Proof of Lemma 5)
    \[
      \frac{M + \sqrt{M^2+4t}}{2} \approx M + \frac{t}{M}
    \]
    we can just use the left hand side
  \item For $T = \lambda_1(\lambda_1 - M)$ the left hand side simplifies to $\lambda_1$
  \item Now our p-value is
    \[
      \frac{P(\chi_k / w_g \geq \lambda_1)}{P(\chi_k / w_g \geq \lambda_2)}
    \]   
\end{itemize}

\subsection{Exact p-value calculation}

\todo Complete this section

We now describe how to calculate our p-value, following the discussion of
group lasso in \cite{tests:adaptive}. For the rest of this section let
$g = \gstar$ be the index of
the group attaining the maximum on line 3 of Algorithm~\ref{algo:fs}.
%\lambda = \norm{X_g^Ty}_2/w_g$ be the value of the maximum, and
%$r = \text{rank}(X_g)$ be the rank of the maximizing group.
For a vector $u \in \real^p$, let $u_h$ denote the coordinates
of $u$ corresponding to the columns of group $h$ in the design matrix $X$.
We can rearrange the columns of $X$ to group these adjacently, so that
\[
u^TX^T = \begin{pmatrix} u_1^T X_1^T & u_2^T X_2^T & \cdots & u_G^TX_G^T \end{pmatrix}
\]
One step of the calculation will be to find an orthonormal basis for the
linear space $\vecsp_g = \{ u \in \real^p : u_g^T X_g^T y = 0, u_h = 0
\text{ for all } h \neq g \}$ so that we can project orthogonally to
this space. If $X_g$ is a single column and $X_g^Ty \neq 0$ (which
should be the case since $g$ maximizes the absolute value of this
quantity), then the
space is trivial and the desired orthogonal projection is the identity.
Otherwise, if $X_g$ has $p_g > 1$ columns the space $\vecsp_g$
generally has dimension $p_g-1$.
% have dimension $r-1$ for $r = \text{rank}(X_g)$. This holds except in
% degenerate cases such as $X_g = 0$ or $r \ll p_g$, but these cases are not
% likely to occur since $\norm{X_g^T y}_2/w_g$ is supposed to be maximized.
% We proceed by forming the $n \times p_g$ matrix
% $X_g - X_g X_g^T y y^T X_g/\norm{X_g^Ty}_2^2$ and performing Gram-Schmidt
% on the first $r-1$ columns. For precise theorems showing that this will
% generally work, see \cite{outerp:indep}.
We compute an orthonormal basis by Gram-Schmidt and form a
$p_g \times p_g$ matrix, which we denote $V_g$, by appending one column
%0's in the coordinates corresponding to all groups $h \neq g$ and to
of zeroes (since Gram-Schmidt only produces $p_g-1$ columns).
With this we are ready to define the projection

\begin{equation}
  \begin{aligned}
    \label{eq:proj}
    P_g &= \Sigma X_gV_g (V_g^T X_g^T \Sigma X_g V_g)^\dagger V_g^TX_g^T \\
   \end{aligned}
\end{equation}
Also define $H_g = (I-P_g)\Sigma$ and the conditional variance

\begin{equation}
  \begin{aligned}
    \label{eq:cvar}
    \sigma^2_g &= y^TX_gX_g^T H_g X_gX_g^Ty / (w_g^2 \norm{X_g^Ty}_2^2) \\
  \end{aligned}
\end{equation}
These simplify when $X_g$ is a single column, in which case $P_g = 0$,
$H_g = \Sigma$, and $\sigma^2_g = X_g^T\Sigma X_g^T/w_g^2$. We now
describe how to compute our p-value in Algorithm~\ref{algo:pval}. Note
that $F_{\chi^2_r}$ denotes the distribution function of a $\chi^2$
random variable with $r$ degrees of freedom.
%Define $U_g = X_g^Ty/(w_g\norm{X_g^Ty}_2)$.

\begin{algorithm}
  \caption{Computing p-value}
  \label{algo:pval}
  \begin{algorithmic}
    \REQUIRE Response $y$, grouped design matrix $X$ with weights, inactive set $A^c$, index $g$ of last group to enter active set $A$.
    \ENSURE Our p-value for the group $g$ entering the model.
    \STATE Compute $H_g$ and $\sigma^2_g$
    \IF{$X_g$ is a single column}
    \STATE $\sigma_g^2 \gets X_g^T\Sigma X_g/w_g^2$
    \STATE $\tilde X_g \gets X_g / w_g \cdot \text{sign}(X_g^Ty)$
    \ELSE
    \STATE $P_g \gets \Sigma XV_g (V_g^T X^T \Sigma X V_g)^\dagger V_g^TX^T$
    \STATE $H_g \gets (I - P_g)\Sigma$
    \STATE $\sigma^2_g \gets y^TX_gX_g^T H_g X_gX_g^Ty / (w_g^2 \norm{X_g^Ty}_2^2)$
    \STATE $\tilde X_g \gets H_g X_g X_g^T y /(\norm{X_g^Ty}_2 w_g)$
    \ENDIF
    \STATE $\lambda \gets \norm{X_g^Ty}_2/w_g$
%    \STATE \COMMENT{Compute the following two $p$-vectors}
    \STATE $a \gets X^T(y - \lambda \tilde X_g)$
    \STATE $b \gets X^T \tilde X_g$
    \STATE Compute solution $(v_-, v_+)$ of \textsc{LinearFractional}(a,b) optimization subproblem
    \STATE $r \gets \text{rank}(X_g)$
    \STATE $u \gets [F_{\chi^2_r}(v^2_-/\sigma_g^2) - F_{\chi^2_r}(\lambda^2/\sigma_g^2)]/[F_{\chi^2_r}(v^2_-/\sigma_g^2) - F_{\chi^2_r}(v^2_+/\sigma_g^2)]$
    \RETURN $u$
  \end{algorithmic}
\end{algorithm}

We next describe the \textsc{LinearFractional} subproblem and its solution. We
gave the problem this name because it originated in the form
\[
\maximize_{h \neq g, \norm{u_h}_2 = 1} \frac{u_h^TX_h^Ty - u_h^TX_h^TX_gX_g^Ty}
{1 - u_g^TX_g^TX_hu_h}
\]
The solution we describe next is to a slightly different problem, and
also incorporates the information that $g$ maximizes $\norm{X_g^Ty}_2/w_g$.
For details see Appendix~\ref{app:closedform} or \cite{tests:adaptive}.

\begin{algorithm}
  \caption{The \textsc{LinearFractional} optimization subproblem}
  \label{algo:linfrac}
  \begin{algorithmic}
    \REQUIRE The $p$-vectors $a, b$ in Algorithm~\ref{algo:pval}, weights, inactive set $A^c$, a small tolerance number
%(we take $1e^{-10}$)
    \ENSURE Solution pair $(v_-, v_+)$.
    \FOR{$h$ in $A^c$}
      \IF{$\norm{b_h}_2 == 0$ or $\norm{a_h}_2/\norm{b_h}_2 < \text{tol}$}
        \STATE $(v^-_h, v^+_h) \gets (0, \infty)$
      \ELSE
        \STATE $\theta_c \gets a_h^Tb_h/(\norm{a_h}_2 \norm{b_h}_2)$
        \STATE $\theta_s \gets \sqrt{1-\theta_c^2}$
        \STATE $\theta \gets \arccos (\theta_c)$
        \STATE $\phi_s \gets \theta_s \norm{b_h}_2 / w_h$
        \IF{$\phi_s > 1$}
          \STATE $(v^-_h, v^+_h) \gets (0, \infty)$
        \ELSE
          \STATE $\phi \gets \arcsin(\phi_s)$
%          \STATE $\phi_2 \gets \pi - \phi_1$
          \STATE $z_\pm \gets s_\pm \norm{a_h}_2 \cos(\phi) /(w_h - s_\pm \norm{b_h}_2 \cos(\theta - \phi))$ for $s_\pm = \pm 1$
          \IF{$\norm{b_h}_2 < w_h$}
            \STATE $(v_h^-, v_h^+) \gets (\max \{ z_+, z_- \}, \infty)$
          \ELSE
            \STATE $(v_h^-, v_h^+) \gets (\min \{ z_+, z_- \}, \max \{ z_+, z_- \})$
          \ENDIF
        \ENDIF
      \ENDIF
    \ENDFOR
    \STATE $v^- \gets \min_h v_h^-$
    \STATE $v^+ \gets \max_h v_h^+$
    \RETURN $(v^-, v^+)$
  \end{algorithmic}
\end{algorithm}

>>>>

\begin{figure}
\label{fig:curved}
\begin{center}
\resizebox{!}{3in}{\input{../figs/curved.pdf_edit_tex}}
\end{center}
A generic selection event, given by the intersection of a list
of quadratic inequalities. Note that the event need not be simply connected. \end{figure}

The slice for any particular inequality is
$$
\begin{aligned}
\lefteqn{
\left\{t: (y+t\eta)^T Q_i (y+t \cdot \eta) + a_i^T(y+t \cdot \eta) \leq b_i\right\}} \\
 & \qquad = \left\{t: t^2 \cdot \eta^TQ_i\eta + t \cdot(2 y^TQ_i\eta + a_i^T\eta) + y^TQ_iy + a_i^Ty - b_i \leq 0 \right\} \\
\end{aligned}
$$
This can be computed easily, and results in either the empty, a single interval (possibly infinite) or the union of 
two disjoint infinite intervals. The intersection over all $I(s)$ is therefore easily computable.
This yields an easily computable form for the slice
\begin{equation}
\label{eq:slice}
\{g^*(y)=g, \eta(g^*(y))=\eta\}.
\end{equation}
In the picture \eqref{eq:curved}, for every $\eta$, the slice \eqref{eq:slice} is a function
of $P_{\eta}^{\perp}y$. This amounts to a proof of the following lemma.

\begin{lemma}
Suppose $S$ is a selection procedure, i.e. a map $S:\real^n \mapsto {\cal S}$
such that for each $s \in S$ \eqref{eq:selection} holds 
and we are given a matrix valued function $X_s \in \real^{n \times p(s)}$ of rank
$k(s)$.
Then, for every $\eta_s \in \real^{p(s)}$ with $\|\eta_s\|_2=1$, the
slice
\begin{equation}
\label{eq:slice:general}
\left\{t: S(y+t \cdot \eta_s)=s, \frac{X_s^Ty}{\|X_s^Ty\|_2}=\eta_s \right\}
\end{equation}
can be described by
a finite union of closed intervals whose endpoints are functions of 
$(P_s^{\perp}y, (P_s- (X_s\eta_s)(X_s\eta_s)^T)y)$ where
$P_s^{\perp}$ is projection on the orthogonal column space of $X_s$.
Denote this set by $E(s, \eta_s, P_s^{\perp}y, (P_s - X_s \eta_s(X_s\eta_s)^T)y)$ and also define
$$
\begin{aligned}
E_+(s, \eta_s, P_s^{\perp}y, (P_s - X_s \eta_s(X_s\eta_s)^T)y) &= \left\{y + t \cdot \eta_s: S(y+t \cdot \eta)=s, \frac{X_s^Ty}{\|X_s^Ty\|_2}=\eta_s \right\} \\
\end{aligned}
$$
\end{lemma}

In turn, this allows to derive a test statistic to test the hypothesis
$H_{0,s}:X_s^T\mu=0$ conditional on $s$ being selected.
\begin{lemma}
\label{eq:test:dbn}
Conditional on $H_{0,s} \cap E_+(s, \eta_s, P_s^{\perp}y, (P_s - \eta_s\eta_s^T)y)$
the following equality holds in distribution
\begin{equation}
\label{eq:chi:truncated}
(X_s\eta_s)^Ty \overset{D}{=} \theta_s \chi_{k(s)} | (X_s\eta_s)^TE_+(s, \eta_s, P_s^{\perp}y, (P_s - \eta_s\eta_s^T)y) 
\end{equation}
where the scale 
$$
\theta_s = \sigma \frac{y^TP_sy}{y^TX_sX_s^Ty}.
$$
\end{lemma}

{\bf Proof:}
For any $s$, decompose the distribution of $y$ as
$$
(Z^{\perp}_s,Z_s) = (P_s^{\perp}y, X_s^Ty).
$$
Under $H_{0,s}:X_s^T\mu=0$, the density of $Z_s$ can be written as
$$
(2 \pi \Sigma_s \sigma^2)^{-k(s)/2} \exp \left(-\frac{1}{2 \sigma^2} z^T\Sigma_s^{-1}z \right)
$$
with $\Sigma_s = X_s^TX_s$.
Transforming to polar coordinates $(R,U)$ yields a density
$$
(2 \pi \Sigma_s \sigma^2)^{-k(s)/2} r^{k(s)-1} \exp \left(-\frac{r^2}{2 \sigma^2} u^T\Sigma_s^{-1}u \right), \qquad r \geq 0, \|u\|_2=1.
$$
Conditioning on $U$ shows that $R=\|X_s^Ty\|_2|U$ has distribution proportional to a $\chi_{r(s)}$. The only thing to determine
is the scale of the $\chi$, which must be $\sigma \|X_s\eta_s\|_2$.

%\subsection{Relation to covariance test}
%
%Consider the simple case for the first covariate to enter the model.
%In this case the covariance test statistic is $T = \lambda_1(\lambda_1 - M)$.
%\todo Does $M = \lambda_2$? Check proof, now that statistic has changed
%
%This is Lemma 5 from \cite{significance:lasso}.
%
%\begin{itemize}
%
%  \item As in LTTT, $T = \lambda_1 (\lambda_1 - M)$ and $M = \lambda_2$
%  \item Convergence to the limiting Exp(1) distribution is too slow
%    \[
%      \frac{P(\chi_k / w_g \geq m + t/m)}{P(\chi_k / w_g \geq m)} \to e^{-t} \text{ as } m \to \infty
%    \]
%    (when the group achieving $\lambda_1$ is group $g$ and has rank $k$)
%  \item The limiting distribution only depends on $T$, but we also observe $M$
%  \item Let's just try the ratio (conditional $\chi_k$ tail probability) evaluated at $T$ and $M$ (it works better)
%  \item Going one step further, instead of using the approximation (see LTTT Proof of Lemma 5)
%    \[
%      \frac{M + \sqrt{M^2+4t}}{2} \approx M + \frac{t}{M}
%    \]
%    we can just use the left hand side
%  \item For $T = \lambda_1(\lambda_1 - M)$ the left hand side simplifies to $\lambda_1$
%  \item Now our p-value is
%    \[
%      \frac{P(\chi_k / w_g \geq \lambda_1)}{P(\chi_k / w_g \geq \lambda_2)}
%    \]   
%\end{itemize}
%
%
%\subsection{Exact p-value calculation}
%
%\todo Complete this section
%
%We now describe how to calculate our p-value, following the discussion of
%group lasso in \cite{tests:adaptive}. For the rest of this section let
%$g = \gstar$ be the index of
%the group attaining the maximum on line 3 of Algorithm~\ref{algo:fs}.
%%\lambda = \norm{X_g^Ty}_2/w_g$ be the value of the maximum, and
%%$r = \text{rank}(X_g)$ be the rank of the maximizing group.
%For a vector $u \in \real^p$, let $u_h$ denote the coordinates
%of $u$ corresponding to the columns of group $h$ in the design matrix $X$.
%We can rearrange the columns of $X$ to group these adjacently, so that
%\[
%u^TX^T = \begin{pmatrix} u_1^T X_1^T & u_2^T X_2^T & \cdots & u_G^TX_G^T \end{pmatrix}
%\]
%One step of the calculation will be to find an orthonormal basis for the
%linear space $\vecsp_g = \{ u \in \real^p : u_g^T X_g^T y = 0, u_h = 0
%\text{ for all } h \neq g \}$ so that we can project orthogonally to
%this space. If $X_g$ is a single column and $X_g^Ty \neq 0$ (which
%should be the case since $g$ maximizes the absolute value of this
%quantity), then the
%space is trivial and the desired orthogonal projection is the identity.
%Otherwise, if $X_g$ has $p_g > 1$ columns the space $\vecsp_g$
%generally has dimension $p_g-1$.
%% have dimension $r-1$ for $r = \text{rank}(X_g)$. This holds except in
%% degenerate cases such as $X_g = 0$ or $r \ll p_g$, but these cases are not
%% likely to occur since $\norm{X_g^T y}_2/w_g$ is supposed to be maximized.
%% We proceed by forming the $n \times p_g$ matrix
%% $X_g - X_g X_g^T y y^T X_g/\norm{X_g^Ty}_2^2$ and performing Gram-Schmidt
%% on the first $r-1$ columns. For precise theorems showing that this will
%% generally work, see \cite{outerp:indep}.
%We compute an orthonormal basis by Gram-Schmidt and form a
%$p_g \times p_g$ matrix, which we denote $V_g$, by appending one column
%%0's in the coordinates corresponding to all groups $h \neq g$ and to
%of zeroes (since Gram-Schmidt only produces $p_g-1$ columns).
%With this we are ready to define the projection
%
%\begin{equation}
%  \begin{aligned}
%    \label{eq:proj}
%    P_g &= \Sigma X_gV_g (V_g^T X_g^T \Sigma X_g V_g)^\dagger V_g^TX_g^T \\
%   \end{aligned}
%\end{equation}
%Also define $H_g = (I-P_g)\Sigma$ and the conditional variance
%
%\begin{equation}
%  \begin{aligned}
%    \label{eq:cvar}
%    \sigma^2_g &= y^TX_gX_g^T H_g X_gX_g^Ty / (w_g^2 \norm{X_g^Ty}_2^2) \\
%  \end{aligned}
%\end{equation}
%These simplify when $X_g$ is a single column, in which case $P_g = 0$,
%$H_g = \Sigma$, and $\sigma^2_g = X_g^T\Sigma X_g^T/w_g^2$. We now
%describe how to compute our p-value in Algorithm~\ref{algo:pval}. Note
%that $F_{\chi^2_r}$ denotes the distribution function of a $\chi^2$
%random variable with $r$ degrees of freedom.
%%Define $U_g = X_g^Ty/(w_g\norm{X_g^Ty}_2)$.
%
%\begin{algorithm}
%  \caption{Computing p-value}
%  \label{algo:pval}
%  \begin{algorithmic}
%    \REQUIRE Response $y$, grouped design matrix $X$ with weights, inactive set $A^c$, index $g$ of last group to enter active set $A$.
%    \ENSURE Our p-value for the group $g$ entering the model.
%    \STATE Compute $H_g$ and $\sigma^2_g$
%    \IF{$X_g$ is a single column}
%    \STATE $\sigma_g^2 \gets X_g^T\Sigma X_g/w_g^2$
%    \STATE $\tilde X_g \gets X_g / w_g \cdot \text{sign}(X_g^Ty)$
%    \ELSE
%    \STATE $P_g \gets \Sigma XV_g (V_g^T X^T \Sigma X V_g)^\dagger V_g^TX^T$
%    \STATE $H_g \gets (I - P_g)\Sigma$
%    \STATE $\sigma^2_g \gets y^TX_gX_g^T H_g X_gX_g^Ty / (w_g^2 \norm{X_g^Ty}_2^2)$
%    \STATE $\tilde X_g \gets H_g X_g X_g^T y /(\norm{X_g^Ty}_2 w_g)$
%    \ENDIF
%    \STATE $\lambda \gets \norm{X_g^Ty}_2/w_g$
%%    \STATE \COMMENT{Compute the following two $p$-vectors}
%    \STATE $a \gets X^T(y - \lambda \tilde X_g)$
%    \STATE $b \gets X^T \tilde X_g$
%    \STATE Compute solution $(v_-, v_+)$ of \textsc{LinearFractional}(a,b) optimization subproblem
%    \STATE $r \gets \text{rank}(X_g)$
%    \STATE $u \gets [F_{\chi^2_r}(v^2_-/\sigma_g^2) - F_{\chi^2_r}(\lambda^2/\sigma_g^2)]/[F_{\chi^2_r}(v^2_-/\sigma_g^2) - F_{\chi^2_r}(v^2_+/\sigma_g^2)]$
%    \RETURN $u$
%  \end{algorithmic}
%\end{algorithm}
%
%We next describe the \textsc{LinearFractional} subproblem and its solution. We
%gave the problem this name because it originated in the form
%\[
%\maximize_{h \neq g, \norm{u_h}_2 = 1} \frac{u_h^TX_h^Ty - u_h^TX_h^TX_gX_g^Ty}
%{1 - u_g^TX_g^TX_hu_h}
%\]
%The solution we describe next is to a slightly different problem, and
%also incorporates the information that $g$ maximizes $\norm{X_g^Ty}_2/w_g$.
%For details see Appendix~\ref{app:closedform} or \cite{tests:adaptive}.
%
%\begin{algorithm}
%  \caption{The \textsc{LinearFractional} optimization subproblem}
%  \label{algo:linfrac}
%  \begin{algorithmic}
%    \REQUIRE The $p$-vectors $a, b$ in Algorithm~\ref{algo:pval}, weights, inactive set $A^c$, a small tolerance number
%%(we take $1e^{-10}$)
%    \ENSURE Solution pair $(v_-, v_+)$.
%    \FOR{$h$ in $A^c$}
%      \IF{$\norm{b_h}_2 == 0$ or $\norm{a_h}_2/\norm{b_h}_2 < \text{tol}$}
%        \STATE $(v^-_h, v^+_h) \gets (0, \infty)$
%      \ELSE
%        \STATE $\theta_c \gets a_h^Tb_h/(\norm{a_h}_2 \norm{b_h}_2)$
%        \STATE $\theta_s \gets \sqrt{1-\theta_c^2}$
%        \STATE $\theta \gets \arccos (\theta_c)$
%        \STATE $\phi_s \gets \theta_s \norm{b_h}_2 / w_h$
%        \IF{$\phi_s > 1$}
%          \STATE $(v^-_h, v^+_h) \gets (0, \infty)$
%        \ELSE
%          \STATE $\phi \gets \arcsin(\phi_s)$
%%          \STATE $\phi_2 \gets \pi - \phi_1$
%          \STATE $z_\pm \gets s_\pm \norm{a_h}_2 \cos(\phi) /(w_h - s_\pm \norm{b_h}_2 \cos(\theta - \phi))$ for $s_\pm = \pm 1$
%          \IF{$\norm{b_h}_2 < w_h$}
%            \STATE $(v_h^-, v_h^+) \gets (\max \{ z_+, z_- \}, \infty)$
%          \ELSE
%            \STATE $(v_h^-, v_h^+) \gets (\min \{ z_+, z_- \}, \max \{ z_+, z_- \})$
%          \ENDIF
%        \ENDIF
%      \ENDIF
%    \ENDFOR
%    \STATE $v^- \gets \min_h v_h^-$
%    \STATE $v^+ \gets \max_h v_h^+$
%    \RETURN $(v^-, v^+)$
%  \end{algorithmic}
%\end{algorithm}
%
